Formulating Regional Typologies

### 2023-11-01 regional_typologies.qmd
small changes
adjust font size

-----------------------------------------------------------------------
## Application of Typology in the Development Masterplan for Integrated Land and Seascape

- The development of an integrated land and sea masterplan (green economic growth)  is structured around planning units.

@@

- The masterplan will include a range of tailored strategies and on-site interventions, reflecting the specific needs of each planning unit.
------------------------------------------------------------------------

>>>>

-----------------------------------------------------------------------

## Application of Typology in the Development Masterplan for Integrated Land and Seascape

::: {style="font-size:26px"}
- The development of an integrated land and sea masterplan (green economic growth) is structured around planning units.

@@

- The masterplan will include a range of tailored strategies and on-site interventions, reflecting the specific needs of each planning unit.
:::
------------------------------------------------------------------------
